% Resume in LaTeX
% Guillermo Salvador Calderon Lopez

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-----------RESUME 2020-----------

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Guillermo Salvador Calderon Lopez} \\ \vspace{1pt}
    \small +52-998-125-0999 $|$ \href{mailto:gscalderon99@hotmail.com}{\underline{gscalderon99@hotmail.com}} $|$ 
    \href{https://github.com/salva-calderon/}{\underline{github.com/salva-calderon}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Monterrey Institute of Technology and Higher Education}{Monterrey, Mexico}
      {B.S. in Computer Science and Technology Engineering}{Expected Graduation Date: June 2023}
      \resumeItemListStart
        \resumeItem{GPA: 97/100}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, C/C++, MATLAB, R} \\
     \textbf{Technologies}{: Git, Android, iOS} \\
     \textbf{Languages}{: Spanish (Native), English (Full Professional), French (Beginner)} \\
    }}
 \end{itemize}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Platform Administrator at Met. Conecta}{Monterrey, Mexico}
      {Company focused on entrepreneurship}{Aug. 2019 –- June 2020}
      \resumeItemListStart
        \resumeItem{Directed 5 entrepreneurs with technology projects, through linkage and proven methodologies in three areas:  innovation, entrepreneurship and training.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------MAJOR SCHOOL PROJECTS-----------
\section{Major School Projects}
\resumeSubHeadingListStart
    \resumeSubheading
      {Streaming Site Menu}{Monterrey, Mexico}
      {OOP Final Project}{June 2020}
      \resumeItemListStart
        \resumeItem{Developed a C++ program that simulates a Streaming Site Menu. This program read 3 CVS files and using features of object-oriented programming generates reports of the movies and series according to their genre, rating and duration.}
      \resumeItemListEnd
      \resumeSubheading
      {Dynamic simulation of projectiles thrown by Popocatepetl}{Monterrey, Mexico}
      {Engineering and Science Modeling Final Project}{Oct. 2019}
      \resumeItemListStart
        \resumeItem{Developed a computational simulation in MATLAB that takes into account the calculation of the trajectories of volcanic objects and the precise place of the crash with an uncertainty of less than 2 percent, which helps to optimize rescue efforts in a volcanic eruption situation.
}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------MAJOR CONTEST AWARDS-----------
\section{Major Contest Awards}
\resumeSubHeadingListStart
    \resumeSubheading
      {Oracle Cup –- Top TEEN Programmer 2019}{Monterrey, Mexico}
      {Solved problems related to number theory, geometry, greedy, using Python}{Oct. 2019}
      \resumeItemListStart
        \resumeItem {Awarded 10th place out of 65 students in my first year of career at Monterrey Institute of Technology and Higher Education.}
      \resumeItemListEnd
      \resumeSubheading
      {Mexican Mathematical Olympiad (OMM)}{Mexico}
      {Solved problems related to geometry, number theory, combinatorics and algebra}{2016 –- 2018}
      \resumeItemListStart
        \resumeItem{Awarded a \textbf{National Honorable Mention} out of the best 6 students from each state in Mexico.}
        \resumeItem{Awarded \textbf{2 Regional Bronze Medals} out of the best 8 students from each state of the south zone in Mexico.}
        \resumeItem{Awarded \textbf{2 Gold State Medals} out of more than 1 thousand students in Quintana Roo.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership}
\resumeSubHeadingListStart
    \resumeSubheading
      {Mexican Mathematical Olympiad in Quintana Roo (OMMQROO) }{Cancun, Mexico}
      {Committee Member: Official Trainer}{Early 2017 -- Present}
      \resumeItemListStart
        \resumeItem{Trained 40 students for one month with intensive courses to develop their skills in geometry, number theory, combinatorics and algebra.}
      \resumeItemListEnd
    \resumeSubheading
      {Board of Directors at UNIDOS}{Cancun, Mexico}
      {Social Project}{2018 -- Present}
      \resumeItemListStart
        \resumeItem{Boosted youth participation in volunteer activities in efforts to promote union and solidarity in society.}
    \resumeItem{In 2019 the project had the participation of 1,500 volunteers and in 2020 more than 5,000 volunteers were registered, but it was canceled due to the pandemic.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}